Ecosystem carbon balance in the Hawaiian Islands under different scenarios of future climate and land use change

### 2021-08-13 Manuscript/HI_Model_ms.Rmd
updated manuscript files

---
title: "Ecosystem carbon balance in the Hawaiian Islands under different scenarios of future climate and land use change"
bibliography: HI_Model.bib
csl: iop.csl
geometry: margin=1in
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \doublespacing
output: 
  pdf_document: 
    latex_engine: xelatex
mainfont: Times New Roman
fontsize: 12pt
urlcolor: blue
nocite: |
  @jacobi_map_2017
---

>>>>

---
title: "Ecosystem carbon balance in the Hawaiian Islands under different scenarios of future climate and land use change"
bibliography: HI_Model.bib
csl: iop.csl
geometry: margin=1in
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \doublespacing
output: 
  pdf_document: 
    keep_tex: yes
    latex_engine: xelatex
mainfont: Times New Roman
fontsize: 12pt
urlcolor: blue
nocite: |
  @jacobi_map_2017
---

### 2021-08-13 Manuscript/HI_Model_ms20210405.Rmd
updated manuscript files

 Net primary production for each simulation cell was calculated as the mean IBIS-derived value for each combination of moisture zone and state type adjusted with a spatially explicit stationary growth multiplier to reflect local variation driven by microclimate [@sleeter_effects_2019]. We calculated this spatial growth multiplier as the NPP anomaly for each simulation cell relative to mean NPP values for each combination of moisture zone and state type based on empirical relationships between total annual NPP and mean annual rainfall or temperature [@schuur_productivity_2003; @del_grosso_global_2008] using Hawaiʻi-specific climate data [@giambelluca_online_2013; @giambelluca_evapotranspiration_2014]. Soil carbon flux to the atmosphere (R~h~) and aquatic soil carbon losses (leaching and overland flow) were estimated as the ratio of the IBIS-derived flux for each combination of moisture zone and state type to the microclimate-adjusted NPP value for each simulation cell. All other carbon flow rates were estimated as the ratio of the mean IBIS-derived flux for each combination of moisture zone and state type to the size of the originating carbon stock at each age [@sleeter_effects_2018; @daniel_integrating_2018]. Climate change impacts on carbon flows were represented by temporal growth and decay multipliers applied to each simulation cell based on mid-century (2049-2069) and end-of-century (2070-2099) statistically downscaled CMIP5 temperature and rainfall projections for the Hawaiian Islands under each of two radiative forcing scenarios [RCP 4.5 and RCP 8.5; @timm_statistical_2015; @timm_future_2017]. The impact of future changes in rainfall and temperature on NPP were represented by annual growth multipliers calculated using empirical NPP models [@schuur_productivity_2003; @del_grosso_global_2008] and climate model projections of temperature and rainfall for each radiative forcing scenario. The effect of future warming on turnover rates of dead organic matter were represented by temporal decay multipliers calculated using Q10 functions and climate model temperature projections for each radiative forcing scenario. We applied a Q10 of 2.0 for wood and soil organic matter decay flows [@kurz_cbm-cfs3:_2009; @sleeter_effects_2019] and a Q10 of 2.17 for litter decay flows [@bothwell_leaf_2014]. Transition-triggered carbon flows resulting from disturbances associated with land use change, timber harvesting, and wildfire were based on values from @don_impact_2011, @selmants_baseline_2017, and @daniel_integrating_2018.

>>>>

 Net primary production for each simulation cell was calculated as the mean IBIS-derived value for each combination of moisture zone and state type adjusted with a spatially explicit stationary growth multiplier to reflect local variation driven by microclimate [@sleeter_effects_2019]. We calculated this spatial growth multiplier as the NPP anomaly for each simulation cell relative to mean NPP values for each combination of moisture zone and state type based on empirical relationships between total annual NPP and mean annual rainfall or temperature [@schuur_productivity_2003; @del_grosso_global_2008] using Hawaiʻi-specific climate data [@giambelluca_online_2013; @giambelluca_evapotranspiration_2014]. Soil carbon flux to the atmosphere (R~h~) and aquatic soil carbon losses (leaching and overland flow) were estimated as the ratio of the IBIS-derived flux for each combination of moisture zone and state type to the microclimate-adjusted NPP value for each simulation cell. All other carbon flow rates were estimated as the ratio of the mean IBIS-derived flux for each combination of moisture zone and state type to the size of the originating carbon stock at each age [@sleeter_effects_2018; @daniel_integrating_2018]. Climate change impacts on carbon flows were represented by temporal growth and decay multipliers applied to each simulation cell based on mid-century (2049-2069) and end-of-century (2070-2099) statistically downscaled CMIP5 temperature and rainfall projections for the Hawaiian Islands under each of two radiative forcing scenarios [RCP 4.5 and RCP 8.5; @timm_statistical_2015; @timm_future_2017]. The impact of future changes in rainfall and temperature on NPP were represented by annual growth multipliers calculated using empirical NPP models [@schuur_productivity_2003; @del_grosso_global_2008] and climate model projections of temperature and rainfall for each radiative forcing scenario. The effect of future warming on turnover rates of dead organic matter were represented by temporal decay multipliers calculated using Q10 functions and climate model temperature projections for each radiative forcing scenario. We applied a Q10 of 2.0 for wood and soil organic matter decay flows [@kurz_cbm-cfs3_2009; @sleeter_effects_2019] and a Q10 of 2.17 for litter decay flows [@bothwell_leaf_2014]. Transition-triggered carbon flows resulting from disturbances associated with land use change, timber harvesting, and wildfire were based on values from @don_impact_2011, @selmants_baseline_2017, and @daniel_integrating_2018.
